The \dealii Library, Version 9.6

### 2024-09-20 9.6/paper.tex
Minor edits.
Extend the description of the TpetraWrappers classes.

In the current release, we have put substantial work into this switch. The following omits the \texttt{LinearAlgebra} prefix for readability.
\begin{itemize}
  \item The \texttt{TpetraWrappers::Vector} class has been overhauled to also allow specifying
    a memory space, and the \texttt{TpetraWrappers::BlockVector} class has been added.
  \item \texttt{TpetraWrappers::SparseMatrix} and \texttt{TpetraWrappers::SparsityPattern} have been implemented mirroring
    the functionality of the \texttt{TrilinosWrappers::SparseMatrix} \\ and \texttt{TrilinosWrappers::SparsityPattern} classes.
  \item Various \texttt{TpetraWrappers::Precondition*} classes have been added largely
    mirroring the exising preconditioners in the \texttt{LinearAlgbera::TrilinosWrappers} namespace.
  \item \texttt{TpetraWrappers::SolverDirect} and \texttt{TpetraWrappers::SolverDirectKLU2}
    have been implemented as direct solvers.
\end{itemize}
Most of the interfaces are usable at this point even if some functionality existing in the \texttt{TrilinosWrappers} classes
is still missing, most noticably a wrapper for an algebraic-multigrid preconditioner.

All the \texttt{TpetraWrappers} classes take \texttt{Number} and \texttt{MemorySpace} template arguments
allowing to control the underlying number type and the memory space used for storing the data. Note that the memory space type
also determines whether \tpetra{} takes advantage of GPUs if \texttt{Kokkos} has been configure with a GPU backend.

>>>>

In the current release, we have put substantial work into this switch,
as outlined below. In the following list, we omit the common namespace
\texttt{LinearAlgebra::} prefix on all mentioned
\texttt{TpetraWrappers} symbols for readability:
\begin{itemize}
  \item The \texttt{TpetraWrappers::Vector} class has been overhauled to also allow specifying
    a memory space, and the \texttt{TpetraWrappers::BlockVector} class has been added.
  \item \texttt{TpetraWrappers::SparseMatrix} and \texttt{TpetraWrappers::SparsityPattern} have been implemented mirroring
    the functionality of the \texttt{TrilinosWrappers::SparseMatrix} \\ and \texttt{TrilinosWrappers::SparsityPattern} classes.
  \item Various \texttt{TpetraWrappers::Precondition*} classes have been added largely
    mirroring the exising preconditioners in the \texttt{LinearAlgbera::TrilinosWrappers} namespace.
  \item \texttt{TpetraWrappers::SolverDirect} and \texttt{TpetraWrappers::SolverDirectKLU2}
    have been implemented as direct solvers.
\end{itemize}
The preconditioner available in the \texttt{TpetraWrappers::Precondition*} classes can be used along with the existing 
iterative solvers, e.g., CG, GMRES, etc.; therefore, the interface is already usable. 
Even if some functionality exists, the \texttt{TrilinosWrappers} classes are missing, most noticably a wrapper for an 
algebraic-multigrid preconditioner.

The design goal was to introduce as few changes as possible for the user to allow for an easy transition to the 
\texttt{TpetraWrappers} classes. 
However, based on the difference between \epetra{} and \tpetra{}, the following changes where necessary:
\begin{itemize}
  \item The constructor for the class \texttt{TrilinosWrappers::MPI::Vector} only required the \texttt{IndexSet locally\_owned}, 
    which describes the set of indices locally owned by the current rank. 
    However, if one wants to create a vector that has read or write access to non-locally owned indices,  the constructor of the 
    \texttt{TpetraWrappers::Vector} requires \texttt{IndexSet locally\_owned}, the \texttt{IndexSet locally\_relevat}, and 
    a boolean flag, whether to initialize the vector in the read-only or the write-only state.
  \item A vector created without providing a \texttt{IndexSet locally\_relevat} is purely local and cannot access non-local indices. 
    Such a vector can not be copied to a vector that can access non-local indices, as the \texttt{IndexSet locally\_relevat} must 
    be provided at creating the vector object.
\end{itemize}

One other important change is that
all the \texttt{TpetraWrappers} classes take \texttt{Number} and \texttt{MemorySpace} template arguments,
which control the underlying number type and memory space. 
By default, the number type is set to  \texttt{double}, and memory is allocated on the CPU, mirroring the 
behavior of the \texttt{TrilinosWrappers}. 
The support for different number types also enables the usage of automatic differentiation-based tools in 
\trilinos{}, such as \texttt{NOX}. 
Additionally, the memory space type determines whether \tpetra{} can utilize GPUs if \kokkos{} is configured 
with a GPU backend. 
To make the automatic differentiation tools of \trilinos{} accessible through the \tpetra{} interface without 
requiring users to have an in-depth understanding of \trilinos{}, additional wrappers for the corresponding 
\trilinos{} packages will be added in future releases. 
Furthermore, further work is needed to fully leverage the GPU backend and unlock its full potential for users.

Moreover, the \tpetra{} interface allows access to more functionality and preconditioners, e.g., \texttt{FROSch}, 
available in \trilinos{}, which will be made accessible through the \texttt{TpetraWrappers} in the future.
